Boundary Labeling for annotated documents

### 2018-03-16 LaTeX/Paper.tex
Paper: Re-wrote explanation of search-space limitation by previous routings, added graphic. Program: No changes.

\change{A \emph{polyline} is a sequence of points $O=p_1, p_2, ...,p_n$, connecting each point to its successor with straight lines. Each point $p \in O$ cannot be equal to any other point in $O$.
We will call a polyline $O$ \emph{monotonically increasing}, if any two vertices $p_i, p_j \in O$ satisfy the following: $\forall p_i, p_j \in O: i<j \iff (X(p_i)\leq X(p_j) \land Y(p_i)\leq Y(p_j)\land p_i \neq p_j)$, where $X(.)$ returns a point's X-coordinate, and $Y(.)$ returns its Y-coordinate.}

@@

\change{These restrictions are implemented as follows: We divided the text $T=\{W,H\}$ into separate lines $L=\{l_1 ,l_2 , ... ,l_n\}$ which are in turn made up of words $w \in W$ and whitespace $h \in H$, which alternate, starting and ending with a word, which creates a sequence $l=(w_1,h_1,w_2, ... , h_{m-1},w_m)$, where $m$ is the number of words in $l$. The width of each line is equal to the text area's total width in characters $(width)$, which means that $m \leq \frac{width}{2}$.} The remaining space between lines is called $S=\{s_1, ... s_{n+1}\}$, with $n$ being the number of lines in $L$. For each $l_i \in L$,  $s_i$ is the space directly above that line. All $s \in S$ are the same height and width, even $s_1$ and $s_{n+1}$, which only have lines on one of their sides. \change{The $s \in S$ and $l \in L$ are arranged in alternating order in the text $T=\{s_1, l_1, s_2, l_2, ..., s_n, l_n, s_{n+1}\}$.}  For each word $w \in W$, we define $R(w)$  as its bounding rectangle, which marks the space leaders aren't allowed to cross. For a graphical representation see Fig.~\ref{fig:wbound}.

@@

The Routing Area will be used to connect each site's path with its source, using OPO-Leaders. Combined with the path \change{$P=\{s, v_1, v_2, ..., v_h, v_b\}; P \subset V; P \cap B = v_b$} leading from the source $s \in S$ to the graph's border $(v_b \in B)$ it creates an unbroken connection between a source and its port, which shall be called a \emph{Source-Port-Path}, or \emph{SP-Path}.

@@

We use a depth-first-search algorithm with the Graph $G$ and the set of sites $V_{ann} \subset V$ as input. The Algorithm prioritizes routing to not yet visited vertices located above the current vertex and terminates either when reaching the right text border or if all possible paths failed to reach the text border, and the resulting SP-path will be monotonically increasing. If the routing for any site $v_{ann} \in V_{ann}$ failed, the algorithm returns $\bot$ for that site. \change{To ensure that routings remain crossing-free, the most recently successfully routed leader is used as a ceiling to the available search space. This means that all vertices that are both above any of that leader's vertices and not between one of that leader's vertices and the border vertices are forbidden to use.} This path is split into two parts: The path within the graph $(P \subset V)$, leading from the source to the text area's border, and the OPO-Leader that connects the text area's border with the Label's port. The former is implemented as a list of vertices $V_{Path} \subset V$ the leader travels through, whereas the latter is determined by the rightmost vertex of $V_{Path}$, the Port, and the location of the P-Segment. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

@@

\begin{proof}
	As discussed in section~\ref{sec:ProbSpec}, each line holds at most $\frac{width}{2}$ words, with an appropriate amount of whitespace in between. Since $width$ is a constant value, the amount of vertices placed is only dependent on the number of lines in the text, therefore $|V|=O(n)$.
	Similarly, each vertex has at most 4 edges, representing the two possible placements of P- or O-Segments starting from that vertex, respectively. Therefore, $|E|=O(n)$. As both the creation of new vertices and edges can be done in a constant amount of time, the overall computation time is in $O(n)$.
\end{proof}

>>>>

A \emph{polyline} is a sequence of points $O=p_1, p_2, ...,p_n$, connecting each point to its successor with straight lines. Each point $p \in O$ cannot be equal to any other point in $O$.
We will call a polyline $O$ \emph{monotonically increasing}, if any two vertices $p_i, p_j \in O$ satisfy the following: $\forall p_i, p_j \in O: i<j \iff (X(p_i)\leq X(p_j) \land Y(p_i)\leq Y(p_j)\land p_i \neq p_j)$, where $X(.)$ returns a point's X-coordinate, and $Y(.)$ returns its Y-coordinate.

@@

These restrictions are implemented as follows: We divided the text $T=\{W,H\}$ into separate lines $L=\{l_1 ,l_2 , ... ,l_n\}$ which are in turn made up of words $w \in W$ and whitespace $h \in H$, which alternate, starting and ending with a word, which creates a sequence $l=(w_1,h_1,w_2, ... , h_{m-1},w_m)$, where $m$ is the number of words in $l$. The width of each line is equal to the text area's total width in characters $(width)$, which means that $m \leq \frac{width}{2}$. The remaining space between lines is called $S=\{s_1, ... s_{n+1}\}$, with $n$ being the number of lines in $L$. For each $l_i \in L$,  $s_i$ is the space directly above that line. All $s \in S$ are the same height and width, even $s_1$ and $s_{n+1}$, which only have lines on one of their sides. The $s \in S$ and $l \in L$ are arranged in alternating order in the text $T=\{s_1, l_1, s_2, l_2, ..., s_n, l_n, s_{n+1}\}$.  For each word $w \in W$, we define $R(w)$  as its bounding rectangle, which marks the space leaders aren't allowed to cross. For a graphical representation see Fig.~\ref{fig:wbound}.

@@

The Routing Area will be used to connect each site's path with its source, using OPO-Leaders. Combined with the path $P=\{s, v_1, v_2, ..., v_h, v_b\}; P \subset V; P \cap B = v_b$ leading from the source $s \in S$ to the graph's border $(v_b \in B)$ it creates an unbroken connection between a source and its port, which shall be called a \emph{Source-Port-Path}, or \emph{SP-Path}.

@@

\begin{figure}
	\captionsetup{justification=centering, margin=0.75cm}
	\centering
	\includegraphics[scale=1]{Ceiling.png}
	\caption{Illustration of the search-space limitation by previous leaders}
	\label{fig:ceil}
\end{figure}

We use a depth-first-search algorithm with the Graph $G$ and the set of sites $V_{ann} \subset V$ as input. The Algorithm prioritizes routing to not yet visited vertices located above the current vertex and terminates either when reaching the right text border or if all possible paths failed to reach the text border, and the resulting SP-path will be monotonically increasing. If the routing for any site $v_{ann} \in V_{ann}$ failed, the algorithm returns $\bot$ for that site. \change{To ensure that routings remain crossing-free, the most recently successfully routed leader $P_last$ is used as a ceiling to the available search space. This means that any vertex above the polyline created by the vertices in $P_last$ and the connection of $P_last$'s source with the text area's border opposite of the label area is forbidden to use. (See als Fig.~\ref{fig:ceil})} This path is split into two parts: The path within the graph $(P \subset V)$, leading from the source to the text area's border, and the OPO-Leader that connects the text area's border with the Label's port. The former is implemented as a list of vertices $V_{Path} \subset V$ the leader travels through, whereas the latter is determined by the rightmost vertex of $V_{Path}$, the Port, and the location of the P-Segment. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

@@

\begin{proof}
	As discussed in Section~\ref{sec:ProbSpec}, each line holds at most $\frac{width}{2}$ words, with an appropriate amount of whitespace in between. Since $width$ is a constant value, the amount of vertices placed is only dependent on the number of lines in the text, therefore $|V|=O(n)$.
	Similarly, each vertex has at most 4 incident edges, representing the two possible placements of P- or O-Segments starting from that vertex, respectively. Therefore, $|E|=O(n)$. As both the creation of new vertices and edges can be done in a constant amount of time, the overall computation time is in $O(n)$.
\end{proof}
